---
title: "Wrangling Kanza Prairie mammal data"
author: "Allison Horst"
date: "5/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(janitor)
library(naniar)
library(skimr)
library(lubridate)
```

**Dataset title:** CSM08 Small mammal host-parasite sampling data for 16 linear trapping transects located in 8 LTER burn treatment watersheds at Konza Prairie

**Data:** https://portal.lternet.edu/nis/mapbrowse?packageid=knb-lter-knz.99.3

**Metadata:** https://portal.lternet.edu/nis/metadataviewer?packageid=knb-lter-knz.99.3

**Citation:** Hope A. 2019. CSM08 Small mammal host-parasite sampling data for 16 linear trapping transects located in 8 LTER burn treatment watersheds at Konza Prairie. Environmental Data Initiative. https://doi.org/10.6073/pasta/69109c56fcf21a30a8d37369cb47f8de. Dataset accessed 5/01/2020.

### Get data & clean:
```{r}
kp <- read_csv(here::here("data","kp_sm_mammals.csv")) %>% 
  clean_names() %>% 
  select(date, watershed, transect, species, total_length:age) %>% 
  filter(species %in% c("SIHI","PMLE","PMMA","MIOC")) %>% 
  mutate(common_name = case_when(
    species == "SIHI" ~ "cotton rat",
    species == "PMLE" ~ "white-footed mouse",
    species == "PMMA" ~ "deer mouse",
    species == "MIOC" ~ "prairie vole"
  )) %>% 
  purrr::map_df(tolower) %>% 
  replace_with_na_all(~.x %in% c("sj","?")) %>% 
  relocate(common_name, .after = species) %>% 
  select(-species, -watershed, -transect) %>% 
  mutate(ear_length = na_if(ear_length, ".")) %>% 
  mutate(date = mdy(date))

write_csv(kp, here::here("data","kp_mammals.csv"))
```

### Read-in new CSV for testing:
```{r}
kp_data <- read_csv(here("data","kp_mammals.csv"))
```



### Counts: 
```{r}
kp_data %>% 
  count(common_name) %>% 
  arrange(-n)

# Four most common species in dataset: 
# SIHI (380): Sigmodon hispidus (cotton rat) - fun fact, first model organism in polio research
# PMLE (313): Peromyscus leucopus (white-footed mouse)
# PMMA (151): Peromyscus maniculatus (N. Am. deer mouse)
# MIOC (127): Microtus ochrogaster (prairie vole)
```

### Visualize total missings
```{r}
vis_miss(kp_data)
```

### Visualize missings by intersection

Only includes variables that have missings. That's cool. 
An upset plot! 
See more: https://cran.r-project.org/web/packages/naniar/vignettes/naniar-visualisation.html
```{r}
gg_miss_upset(kp_data, nsets = 7)
```

Cool!!!! 

What about trying to see differences in missings by species? `gg_miss_fct()`! So cool...

```{r}
gg_miss_fct(kp_data, fct = common_name)
```

